---
title: "Model"
output:
  html_notebook: default
  pdf_document: default
---

```{r}
library(gapminder)
library(tidyverse)
library(ggformula)
library(ggfortify)
library(gapminder)
library(GGally)
library(ISLR)
library(tidyr)
library(dataPreparation)
library(partykit)
library(rpart)
library(mdsr)
library(rpart.plot)
library(interplot)
library(tidyverse)
library(coefplot)
library(gridExtra)
library(reshape2)
library(boot)
```
# Modeling!

I apologize for the mess that is the 180 lines above this. Here is what I want to focus on for the linear regression and data analysis.

Can Universities be used to predict the Documents of a nation.
Can Population be use dto predict the Documents of a nation.
Do both Universities and Population predict the "rank" of a nation.
Finally, I want to see if univerities and population can predict documents produced

```{r}
TDS20$Unversities <- as.numeric(TDS20$Unversities)
TDS20$Rank <- as.character(TDS20$Rank)
TDS20$Population <- as.numeric(TDS20$Population)

TDS2$Unversities <- as.numeric(TDS2$Unversities)
TDS2$Rank <- as.numeric(TDS2$Rank)
TDS2$Population <- as.numeric(TDS2$Population)

```

```{r}
TDS20 <-filter(TDS2, Rank <= 20)
```

```{r}

ggplot(TDS20, aes(x = Documents, y = Unversities , color = Country)) + geom_point()
ggplot(TDS20, aes(x = Documents, y = Population , color = Country)) + geom_point()

```
Lets being our linear regression. This regression is only for the top 20 countries and is not represenatitive of the whole data set.
```{r}
TDS20_lm <- lm(Documents ~ Unversities + Population + MVW, data = TDS2POPWVM)
summary(TDS20_lm)
```
```{r}
TDS20_lm1 <- lm(Documents ~ Unversities*Population*MVW,data=TDS2POPWVM)
summary(TDS20_lm1)
```

```{r}
predict(TDS20_lm,data.frame(Unversities=c(50),Population=c(60)),interval = "prediction")
```

```{r}
summary(TDS20_lm)
```


Okay now I am goin to todo the whole data set instead of the top 20

```{r}
TDS2_lm <- lm(Documents ~ Unversities + Population, data = TDS2)
TDS2_lm1 <- lm(Documents ~ Unversities*Population,data=TDS2)
summary(TDS2_lm1)
summary(TDS2_lm)
```
```{r}
train_index <- sample(1:nrow(TDS2),0.8*nrow(TDS2))
test_index <- sample(1:nrow(TDS2),0.2*nrow(TDS2))
```

okay I am going to make a training set and then a test set

## NEED TO FIX THIS
```{r}
Xtrain_TDS2 <- TDS2[train_index,] %>% select(-Documents)
Ytrain_TDS2 <- TDS2[train_index,] %>% select(Documents)

Xtest <- TDS2[test_index,] %>% select (-Documents)
Ytest <- TDS2[test_index,] %>% select(Documents)
```
scaling the data
```{r}

scales <- build_scales(dataSet = Xtrain_TDS2, cols = c("Population", "Unversities"), verbose = TRUE)

print(scales)

Xtrain_TDS2 <- fastScale(dataSet = Xtrain_TDS2, scales = scales, verbose = TRUE)
Xtest <- fastScale(dataSet = Xtest, scales = scales, verbose = TRUE)
```
```{r}
head(Xtrain_TDS2)
```
I have a question: Dont I need to scale the y variable as well?
```{r}
TDS21 <- cbind(Xtrain_TDS2,Ytrain_TDS2)

```
```{r}
tally(~Documents,data=TDS21,format="percent")
```
```{r}
rt.TD <-rpart(Documents ~ Population + Unversities, data = TDS21)
```

```{r}
split <- 0.50
TDS21 <- TDS21 %>% mutate(hi_number_universities = Unversities >= split)
TDS21 %>% ggplot(mapping = aes(x=Unversities,y=Documents,color = "lightblue","aquamarine")) + 
  geom_count(aes(color=hi_number_universities), position = position_jitter(width=0,height=0.1),alpha=0.5) + 
  geom_vline(xintercept = split, color="slateblue",lty=2) + 
  scale_x_log10()
```

```{r}
prp(rt.TD, extra =101 , box.col ="orange" , split.box.col = "grey")
```

```{r}
printcp(rt.TD)
```


```{r}
TDS21 %>% ggplot(aes(x= Population, y = Documents )) + geom_point() + stat_smooth(method="lm")
```
```{r}
TDS21 %>% ggplot(aes(x= Unversities, y = Documents )) + geom_point() + stat_smooth(method="lm")
```

```{r}
interplot(m = TDS2_lm1 , var1 = "Population", var2 = "Unversities", hist = TRUE) + geom_line(color = "blue") + geom_hline(yintercept = 0, linetype = "dashed") 
```

```{r}

interplot(m = TDS2_lm1 , var1 = "Unversities", var2 = "Population", point = T) +   theme(axis.text.x  = element_text(angle=90))
```
```{r}

coefplot(TDS2_lm1)
```
```{r}
coefplot(TDS2_lm)
```



```{r}
TDS2POP <- TDS2 %>% left_join(population_total, by = "Country")
TDS2POPWVM <- TDS2POP %>% left_join(mean_years_in_school_women_percent_men_25_to_34_years, by = "Country")
```

```{r}
TDS2POPWVM
```

```{r}
TDS3 <- mutate(TDS2POPWVM,MVW10 = ifelse(TDS2POPWVM$MVW > 100,1,0))
```

```{r}
ggplot(data = TDS3) + geom_bar(aes(x=MVW10))
```
```{r}
ggplot(data = TDS3) + geom_point(aes(x=MVW10,y=Documents))
```
